\begin{prob}\ \\
    a.  The class median on the quiz you designed and wrote is 25\%.\\
    b. The class median on the lecturer's exam is 25\%.
\end{prob}

\begin{solution}\ \\
    a. I will reflect on my teaching and my quiz design too see where the students lost most of their points. If possible, I will try to curve the quiz score.\\
    b. If lecturer wants to discuss about I will be happy to give my input. If lecturer wants I can take some revision tutorial.
\end{solution}

\begin{prob}
    A student tells you that your grading is too harsh. What if several students tell you that?
\end{prob}

\begin{solution}
    I will show them where they lost their points and for which step. Since the grading is universal I cannot change it. Also I will reflect on my grading if their cencern is genuine. 
\end{solution}

\begin{prob}
    A day after group grading exams with several other TAs, a student's midterm is missing. You
remember that the student took the exam. 
\end{prob}

\begin{solution}
    I will look for the quiz paper again. I will consult with lecturer/coordinator about how to go about it, possible solutions maybe allowing the student to take the exam again/ giving the student average score.
\end{solution}

\begin{prob}\ \\
    a. A student asks to go to the restroom during a quiz/midterm.\\
    b. A student says he can do better on quizzes and tests if he wears headphones.\\
    c.  A student shows up to class halfway through a quiz. What if it happens during a midterm? 
\end{prob}

\begin{solution}\ \\
    a. If he asks towards the end of the quiz I will asks if they can hold. If not I will let them go and would not allow to take any devices with them.\\
    b. I would strictly not allow the student to use headphones.\\
    c. I will allow the student to sit for the exam but the student would not get any extra time. In the case where it is midterm and the excuse is genuine, I will give the student another sheet to finish the midterm at the end of the exam and consult with the instructor/co-ordinator about what need to be done.
\end{solution}

\begin{prob}
    A student complains that you gave him no credit when his answer was right. When you look at his
paper, you notice one of the following:\\
a. None of the work was right, but the numerical answer was.\\
b. There is no work, just the answer.\\
c. His answer looks perfect. In fact, it looks exactly like the solution you showed the class right after
you handed the papers back.
\end{prob}

\begin{solution}\ \\
    a. I will give him the points allotted for the right answer in the rubric.\\
    b. I will give him the points allotted for the right answer in the rubric.\\
    c. I will give him the points for right answer and work giving the student the benefit of doubt. I will let the instructor know about my suspicion of cheating and have his answers recorded (photocopied) from that point onward.
    d. I will give him the correct points.
\end{solution}

\begin{prob}\ \\
    a. A parent calls you, asking about their daughter’s performance in the class. How do you respond?\\
    b.  An academic advisor emails you, asking about a student’s performance in the class. How do you
respond?\\
    c. A student emails asking you to reply with their scores. How do you respond?
\end{prob}

\begin{solution}\ \\
    a. I will respond with, ``I am not legally allowed to say anything.''
    b. I will most likely defer my decision to course co-ordinator.
    c. I will first ask if they cannot see their grades on the carmen/gradescope. If not and if the email is from osu.edu then I will reply with their grades (probably after consulting with the co-ordinator). 
\end{solution}

\begin{prob}
    A student tells you that his roommate is taking the same class from someone else and they're doing
grades/tests/homework/etc. differently. 
\end{prob}

\begin{solution}
    I will let the course co-ordinator know about the concern.
\end{solution}

\begin{prob}
    Several students complain to you that there is way too much homework assigned. What if it’s only one
student who complains?
\end{prob}

\begin{solution}
    If several students complain then I will let the instructor know about the concern. If there is only one student then I ask if he wants to take lower courseload.
\end{solution}

\begin{prob}
    You collect homework every Thursday, but half of the students in your class turn it in late or not at all.
Another fourth of the students turn in incomplete work. According to the lecturer's syllabus, the homework
counts for 20\% of the students' final grade. 
\end{prob}

\begin{solution}
    I will say to the whole class that the homework counts for 20\% of the final grade and they should take it more seriously. I will also warn them that from henceforth the late homework will be marked late.
\end{solution}